Data_visualization

### 2018-06-25 Rmd/Data_visualization.Rmd
changes

#read data and cleaning
pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
pein_seed_set <- pein_seed_set[-c(42,47,49),]

@@

#Taking out species that weren't used
some_seed_set <- read.csv("Data/species_seed_set/SOME_seed_set.csv", sep=";")
some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")

@@

#
##
###
#C. ANNUUM 
###
##
#
caan_seed_set <- read.csv("Data/species_seed_set/CAAN_seed_set.csv", sep=";")

@@

soly_seed_set <- read.csv("Data/species_seed_set/SOLY_seed_set.csv", sep=";")
soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

>>>>

#read data and cleaning
pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
pein_seed_set <- pein_seed_set[-c(42,47,49),]

@@

#Taking out species that weren't used
some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")

@@

#
##
###
#C. ANNUUM 
###
##
#
caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")

@@

soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
